---
title: "GNG Analysis"
author: "Mindy Ross"
date: "Updated `r Sys.Date()`"
output: bookdown::html_document2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

# Data processing

<!-- SMS scores were matched to GNG task dates by matching the nearest SMS date to the GNG task date up to 7 days apart. If there were two SMS dates the same number of days apart, the mean scores were taken. -->

Interview scores were matched to GNG task by matching the GNG date to the week during which the interviews were taken.

<!-- Self-report scores were matched to GNG task by matching the GNG date to the month the self-reports reflected. -->

```{r}
# import libraries
library(readr)
library(tidyverse)
library(tableone)
library(lmerTest)
library(sjPlot)
library(effects)
library(ggpubr)


# read in GNG file
f <- '/home/mindy/Desktop/BiAffect-iOS/vanMeter/gng/gng_interview_processed_output-v5.csv'
dfRaw <- read.csv(f)
# dfRaw$sex <- factor(dfRaw$sex)
dfRaw$gender <- factor(dfRaw$gender)
dfRaw$hour <-as.numeric(lubridate::hour(dfRaw$sessionTimestampLocal))
dfRaw$hour <- lubridate::hour(dfRaw$sessionTimestampLocal)
dfRaw$hour2 <- ifelse(dfRaw$hour == 0,24,dfRaw$hour)
# add 1 sec as the correct no-go rxn time
dfRaw$rxnTimeToPlot <- with(dfRaw, ifelse((go == 'False') & (incorrect == 'False'), 1, timeToThreshold_all))

set.seed(123)
dfPlot <- dfRaw %>% filter((rxnTimeToPlot >= 0.2) & (rxnTimeToPlot <= 1) & (hour2 > 6)) %>% # filter out rxn times < 0.2 and > 1 sec, and between 0100 to 0700
              mutate(trial_type = factor(ifelse((go=='True')&(incorrect=='False'), 0, #correct go
                                         ifelse((go=='False')&(incorrect=='True'), 1, #incorrect no go
                                         ifelse((go=='False')&(incorrect=='False'), 2, NA))), # correct no go
                    levels = c(0,1,2), labels = c('correct_go_trial','incorrect_noGo_trial','correct_noGo_trial'))) %>% 
                    ungroup() #%>% #group_by(userID) %>% mutate(hour_range = max(hour) - min(hour)) %>% 
                    # filter((hour_range >= 5) & (max(taskNumber) >= 3))
                     #%>% ungroup() %>%
                     # drop_na(age)
                                                                                                

dfRxn <- dfRaw %>% filter((timeToThreshold_all >= 0.2) & (timeToThreshold_all <= 1) & (hour2 >= 6) & (gender != 3)) %>% # filter out rxn times < 0.2 and > 1 sec, and between 0100 to 0700
                mutate(rxnTime =log(timeToThreshold_all),
                     rxnTime_shuffled = sample(rxnTime),
                     trial_type = factor(ifelse((go=='True'), 0,1),
                                  levels = c(0,1), labels = c('Go Trial','No-Go Trial'))) %>% 
                ungroup() %>% #group_by(userID) %>% mutate(hour_range = max(hour2) - min(hour2)) %>% 
                          #filter((hour_range >= 5) & (max(taskNumber) >= 3)) %>% ungroup() %>% 
                 drop_na(interview_dep_score,age)

# dfRxnSR <- dfRaw %>% filter((timeToThreshold_all >= 0.2) & (timeToThreshold_all <= 1) & (hour2 >= 6)) %>% 
#                 mutate(rxnTime =log(timeToThreshold_all),
#                      rxnTime_shuffled = sample(rxnTime),
#                      trial_type = factor(ifelse((go=='True'), 0,1),
#                                   levels = c(0,1), labels = c('Go Trial','No-Go Trial'))) %>% 
#                 ungroup %>% #group_by(userID) %>% mutate(hour_range = max(hour2) - min(hour2)) %>% 
#                           #filter((hour_range >= 5) & (max(taskNumber) >= 3)) %>% ungroup() %>% 
#                  drop_na(age, sms_sleep,self_report_dep_score) %>%
#           select(-c(interview_dep_score,interview_anx_score, interview_SI_score, interview_mania_score, timezone))

set.seed(1234)
dfAccuracy <- dfRaw %>% filter((go == 'False') & (hour2 > 6) & (gender != 3)) %>% # filter out go trials and between midnight to 0700
                mutate(nogo_flag = factor(ifelse(incorrect == 'False',1,0),levels=c(0,1),labels=c('Incorrect','Correct')), #incorrect=0, correct=1
                       nogo_flag_shuffled = sample(nogo_flag)) %>%
              ungroup %>% #group_by(userID) %>% mutate(hour_range = max(hour2) - min(hour2)) %>% 
                          #filter((hour_range >= 5) & (max(taskNumber) >= 3)) %>% ungroup() %>% 
                 drop_na(interview_dep_score,age)

# dfAccuracySR <- dfRaw %>% filter((go == 'False') & (hour2 > 6)) %>% 
#                 mutate(nogo_flag = factor(ifelse(incorrect == 'False',1,0),levels=c(0,1),labels=c('Incorrect','Correct')), #incorrect=0, correct=1
#                        nogo_flag_shuffled = sample(nogo_flag)) %>%
#               ungroup %>% #group_by(userID) %>% mutate(hour_range = max(hour2) - min(hour2)) %>% 
#                           #filter((hour_range >= 5) & (max(taskNumber) >= 3)) %>% ungroup() %>% 
#                  drop_na(age, sms_sleep, self_report_dep_score)

# interview data summary table
dfTab <- dfRxn %>% group_by(userID) %>%
                summarise(age = unique(age),
                          # sex = unique(sex),
                          gender = unique(gender),
                          # sleep = mean(sms_sleep),
                          # SI = mean(sms_SI),
                          # desire = mean(sms_desire),
                          # intent = mean(sms_intent),
                          # self_harm = mean(sms_self_harm),
                          interview_dep = mean(interview_dep_score),
                          interview_mania = mean(interview_mania_score),
                          interview_anxiety = mean(interview_anx_score),
                          interview_SI = mean(interview_SI_score),
                          nGNG = max(taskNumber))

# # self-report data summary table
# dfTabSR <- dfRxnSR %>% group_by(userID) %>%
#                 summarise(age = unique(age),
#                           sex = unique(sex),
#                           gender = unique(gender),
#                           sleep = mean(sms_sleep),
#                           SI = mean(sms_SI),
#                           desire = mean(sms_desire),
#                           intent = mean(sms_intent),
#                           self_harm = mean(sms_self_harm),
#                           SR_dep = mean(self_report_dep_score),
#                           SR_mania = mean(self_report_mania_score),
#                           SR_anxiety = mean(self_report_anx_score),
#                           nGNG = max(taskNumber))

# colSums(is.na(dfAccuracySR))
# colSums(is.na(dfRxnSR))
```

## Assessment/GNG Summary

Number of participants varied based on use of interview or self-report variables due to missing values, so separate models were created using one or the other assessment type.

### Interview Variables

```{r}
tab3 <- CreateTableOne(data = subset(dfTab, select=-c(userID)))
ptables <- print(tab3,  quote = FALSE, noSpaces = TRUE, printToggle = FALSE, test = TRUE, showAllLevels = FALSE, missing = FALSE, varLabels = TRUE )
ptables
```

<!-- ### Self-Report Variables -->

<!-- ```{r} -->
<!-- tab3sr <- CreateTableOne(data = subset(dfTabSR, select=-c(userID))) -->
<!-- ptablessr <- print(tab3sr,  quote = FALSE, noSpaces = TRUE, printToggle = FALSE, test = TRUE, showAllLevels = FALSE, missing = FALSE, varLabels = TRUE ) -->
<!-- ptablessr -->
<!-- ``` -->

## GNG distributions

**Hourly task distribution**

```{r}
hist(dfRaw$hour, breaks=25)
```

GNG tasks tend to be completed between the hours of 6-24 (0600-0059). Data filtered in model to only include tasks completed during these hours.

**GNG Reaction Time**

All GNG reaction times (correct and incorrect trials) following filtering to between 0.2 - 1 sec.

```{r}
hist(exp(dfRxn$rxnTime))
```

GNG reaction time per trial (correct and incorrect trials) was logged in the models

```{r}
hist(dfRxn$rxnTime)
```

**Comparison of reaction time by trial type**

```{r}
dfRxn %>% group_by(trial_type) %>% summarise(mean_reaction_time = mean(exp(rxnTime)),
                                             median_reaction_time = median(exp(rxnTime)),
                                             min_reaction_time = min(exp(rxnTime)),
                                             max_reaction_time = max(exp(rxnTime)),
                                             q1 = quantile(exp(rxnTime), .25),
                                             q3 = quantile(exp(rxnTime), .75),
                                             std = sd(exp(rxnTime)))
```

```{r}
ggplot(dfRxn, aes(x=exp(rxnTime), group = trial_type)) + 
  geom_boxplot(aes(fill=trial_type)) +
  xlab("Reaction Time")+
  ylab("Trial Type")+
  theme_bw()+
  theme(text=element_text(face="bold", size=12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill = NA, colour = "NA"),
        axis.line = element_line(size = 1, colour = "grey80"),
        legend.title=element_blank())
```

## Spaghetti Plots

Correct no-go trials given a reaction time of 1 sec in the plots below to visualize their frequency relative to the other trials with reaction times. Incorrect go trials were not plotted.

```{r,fig.width=12,fig.height=12}
ggplot(dfPlot, aes(x=jitter(hour2), y=jitter(rxnTimeToPlot), trial_type)) + 
      geom_point(size=0.25, aes(color=trial_type, shape=trial_type), alpha=0.7) + 
      scale_color_manual(values=c('#56B4E9','red','chartreuse4')) +
      scale_shape_manual(values=c(3,19,3)) +
      ylab('Reaction Time (s)') + xlab('Hour')+
      facet_wrap(~userID)
```

# Regression Analyses

## No-Go Trial Accuracy

Logistic regression model

### Interview Variables

<!-- 12 participants -->

```{r}
model1Nogo <- glm(nogo_flag ~ scale(age) + gender +
                    #scale(sms_sleep) + #scale(sms_SI) + 
                     scale(interview_SI_score) +
                    # scale(sms_self_harm) + 
                    scale(interview_dep_score) +
                      #scale(interview_anx_score) + #scale(interview_mania_score) +
                      scale(log(taskNumber)),# + poly(hour2,2, raw=FALSE), 
                  data = dfAccuracy, family = 'binomial')
summary(model1Nogo)
```

#### Check for multicolinearity 

```{r}
car::vif(model1Nogo)
```

<!-- ### Self Report Variables -->

<!-- 12 participants -->

<!-- ```{r} -->
<!-- model1NogoSR <- glm(nogo_flag ~ scale(age) + #gender + -->
<!--                       scale(sms_sleep) +  -->
<!--                        # scale(sms_SI) + #scale(sms_self_harm) + -->
<!--                     scale(self_report_dep_score) + -->
<!--                       scale(self_report_anx_score) + -->
<!--                        # scale(self_report_mania_score) + -->
<!--                       scale(log(taskNumber)),# + poly(hour2,2, raw=FALSE), -->
<!--                     data = dfAccuracySR, family = 'binomial') -->
<!-- summary(model1NogoSR) -->
<!-- ``` -->

<!-- #### Check for multicolinearity  -->

<!-- ```{r} -->
<!-- car::vif(model1NogoSR) -->
<!-- ``` -->

### Model Summary

```{r}
tab_model(model1Nogo,digits=3, digits.re = 3,show.ci=FALSE, show.loglik = TRUE, show.obs = TRUE, show.ngroups = TRUE, show.icc=TRUE)
```

<!-- Note: Orthogonal polynomials of hour were fitted in the model, so their model estimates/odds ratios are uninterpretable. -->

<!-- ### Task Number -->

<!-- Model with interview variables -->

<!-- ```{r} -->
<!-- effectNumNogo <- as.data.frame(effects::Effect('taskNumber', model1NogoSR)) -->
<!-- ggplot(data=effectNumNogo, aes(x=taskNumber, y=fit))+ -->
<!--   geom_line(size=1)+ -->
<!--   geom_ribbon(aes(ymin=lower, ymax=upper),alpha=.2) + -->
<!--   xlab("Task Number")+ -->
<!--   ylab("No-Go Trial Accuracy")+ -->
<!--   theme_bw()+ -->
<!--   theme(text=element_text(face="bold", size=12), -->
<!--         panel.grid.major = element_blank(), -->
<!--         panel.grid.minor = element_blank(), -->
<!--         panel.border = element_rect(fill = NA, colour = "NA"), -->
<!--         axis.line = element_line(size = 1, colour = "grey80"), -->
<!--         legend.title=element_blank()) -->
<!-- ``` -->

<!-- ### SMS SI -->

<!-- Model with self-report variables -->

<!-- ```{r} -->
<!-- effectNumNogo <- as.data.frame(effects::Effect('sms_SI', model1NogoSR)) -->
<!-- ggplot(data=effectNumNogo, aes(x=sms_SI, y=fit))+ -->
<!--   geom_line(size=1)+ -->
<!--   geom_ribbon(aes(ymin=lower, ymax=upper),alpha=.2) + -->
<!--   xlab("SMS SI")+ -->
<!--   ylab("No-Go Trial Accuracy")+ -->
<!--   theme_bw()+ -->
<!--   theme(text=element_text(face="bold", size=12), -->
<!--         panel.grid.major = element_blank(), -->
<!--         panel.grid.minor = element_blank(), -->
<!--         panel.border = element_rect(fill = NA, colour = "NA"), -->
<!--         axis.line = element_line(size = 1, colour = "grey80"), -->
<!--         legend.title=element_blank()) -->
<!-- ``` -->

<!-- ### SMS Self-Harm -->

<!-- Model with self-report variables -->

<!-- ```{r} -->
<!-- effectNumNogo <- as.data.frame(effects::Effect('sms_self_harm', model1NogoSR)) -->
<!-- ggplot(data=effectNumNogo, aes(x=sms_self_harm, y=fit))+ -->
<!--   geom_line(size=1)+ -->
<!--   geom_ribbon(aes(ymin=lower, ymax=upper),alpha=.2) + -->
<!--   xlab("SMS Self-Harm")+ -->
<!--   ylab("No-Go Trial Accuracy")+ -->
<!--   theme_bw()+ -->
<!--   theme(text=element_text(face="bold", size=12), -->
<!--         panel.grid.major = element_blank(), -->
<!--         panel.grid.minor = element_blank(), -->
<!--         panel.border = element_rect(fill = NA, colour = "NA"), -->
<!--         axis.line = element_line(size = 1, colour = "grey80"), -->
<!--         legend.title=element_blank()) -->
<!-- ``` -->

<!-- ### Self-Report Anxiety -->

<!-- Model with self-report variables -->

<!-- ```{r} -->
<!-- effectNumNogo <- as.data.frame(effects::Effect('self_report_anx_score', model1NogoSR)) -->
<!-- ggplot(data=effectNumNogo, aes(x=self_report_anx_score, y=fit))+ -->
<!--   geom_line(size=1)+ -->
<!--   geom_ribbon(aes(ymin=lower, ymax=upper),alpha=.2) + -->
<!--   xlab("Self-Report Anxiety")+ -->
<!--   ylab("No-Go Trial Accuracy")+ -->
<!--   theme_bw()+ -->
<!--   theme(text=element_text(face="bold", size=12), -->
<!--         panel.grid.major = element_blank(), -->
<!--         panel.grid.minor = element_blank(), -->
<!--         panel.border = element_rect(fill = NA, colour = "NA"), -->
<!--         axis.line = element_line(size = 1, colour = "grey80"), -->
<!--         legend.title=element_blank()) -->
<!-- ``` -->

## Reaction Time

Regression model

### Interview variables

<!-- 12 participants -->

```{r}
model1Rxn <- lm(rxnTime ~ scale(age) + gender +
                    #scale(sms_sleep) + scale(sms_SI) + 
                  scale(interview_SI_score) +
                  #scale(sms_self_harm) +
                    scale(interview_dep_score) +
                      # scale(interview_anx_score) + #scale(interview_mania_score) +
                    trial_type + scale(log(taskNumber)),# + poly(hour2,2, raw=FALSE),
                  data = dfRxn)
summary(model1Rxn)
```

#### Check for multicolinearity 

```{r}
car::vif(model1Rxn)
```

<!-- ### Self-Report Variables -->

<!-- 12 participants -->

<!-- ```{r} -->
<!-- model1RxnSR <- lm(rxnTime ~ scale(age) + #gender + -->
<!--                     scale(sms_sleep) + #scale(sms_SI) +  -->
<!--                     scale(self_report_dep_score) + -->
<!--                     scale(self_report_anx_score) + #scale(self_report_mania_score) + -->
<!--                     trial_type + scale(log(taskNumber)),# + poly(hour2,2, raw=FALSE), -->
<!--                   data = dfRxnSR) -->
<!-- summary(model1RxnSR) -->
<!-- ``` -->

<!-- #### Check for multicolinearity  -->

<!-- ```{r} -->
<!-- car::vif(model1RxnSR) -->
<!-- ``` -->

### Model Summary

```{r}
tab_model(model1Rxn,digits=3, digits.re = 3,p.val = 'satterthwaite',show.ci=FALSE, show.loglik = TRUE, show.obs = TRUE, show.ngroups = TRUE, show.icc=TRUE)
```

### Age

```{r}
effectTrialRxn <- as.data.frame(Effect(c('age'), model1Rxn))
ggplot(data=effectTrialRxn, aes(x=age, y=exp(fit)))+
  geom_line(size=1)+
  geom_ribbon(aes(ymin=exp(lower), ymax=exp(upper)),alpha=.2) +
  xlab("Age")+
  ylab("GNG Reaction Time (s)")+
  theme_bw()+
  theme(text=element_text(face="bold", size=12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill = NA, colour = "NA"),
        axis.line = element_line(size = 1, colour = "grey80"),
        legend.title=element_blank())
```

### Gender

```{r}
effectTrialRxn <- as.data.frame(Effect(c('gender'), model1Rxn))
ggplot(data=effectTrialRxn, aes(x=gender, y=exp(fit)))+
  geom_point(size = 4)+
  geom_errorbar(aes(ymin=exp(lower), ymax=exp(upper)),alpha=.5, size = 1) +
  xlab("Gender")+
  ylab("GNG Reaction Time (s)")+
  theme_bw()+
  theme(text=element_text(face="bold", size=12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill = NA, colour = "NA"),
        axis.line = element_line(size = 1, colour = "grey80"),
        legend.title=element_blank())
```

### Trial Type

```{r}
effectTrialRxn <- as.data.frame(Effect(c('trial_type'), model1Rxn))
ggplot(data=effectTrialRxn, aes(x=trial_type, y=exp(fit)))+
  geom_point(size = 4)+
  geom_errorbar(aes(ymin=exp(lower), ymax=exp(upper)),alpha=.5, size = 1) +
  xlab("Trial Type")+
  ylab("GNG Reaction Time (s)")+
  theme_bw()+
  theme(text=element_text(face="bold", size=12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill = NA, colour = "NA"),
        axis.line = element_line(size = 1, colour = "grey80"),
        legend.title=element_blank())
```

### Interview SI Score

```{r}
effectTrialRxn <- as.data.frame(Effect(c('interview_SI_score'), model1Rxn))
ggplot(data=effectTrialRxn, aes(x=interview_SI_score, y=exp(fit)))+
  geom_line(size=1)+
  geom_ribbon(aes(ymin=exp(lower), ymax=exp(upper)),alpha=.2) +
  xlab("Interview SI Score")+
  ylab("GNG Reaction Time (s)")+
  theme_bw()+
  theme(text=element_text(face="bold", size=12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill = NA, colour = "NA"),
        axis.line = element_line(size = 1, colour = "grey80"),
        legend.title=element_blank())
```

### Interview Depression Score

```{r}
effectTrialRxn <- as.data.frame(Effect(c('interview_dep_score'), model1Rxn))
ggplot(data=effectTrialRxn, aes(x=interview_dep_score, y=exp(fit)))+
  geom_line(size=1)+
  geom_ribbon(aes(ymin=exp(lower), ymax=exp(upper)),alpha=.2) +
  xlab("Interview Depression Score")+
  ylab("GNG Reaction Time (s)")+
  theme_bw()+
  theme(text=element_text(face="bold", size=12),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(fill = NA, colour = "NA"),
        axis.line = element_line(size = 1, colour = "grey80"),
        legend.title=element_blank())
```
